Augmentation of a Model Historical Harpsichord Mechanism for Haptic Enabled Interaction

### 2025-01-17 src/main.tex
move acknowledgments to main
rm tightlist

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.

\section{Ethical Standards}\label{ethical-standards}

% \begin{anonsuppress}

This work was performed at \anon{San Colombano}
To ensure objectivity and transparency in research and to ensure that
accepted principles of ethical and professional conduct have been
followed, authors must include a section ``Ethical Standards'' before
the References. This section should include (if relevant): information
regarding sources of funding, potential conflicts of interest (financial
or non-financial), informed consent if the research involved human
participants, statement on welfare of animals if the research involved
animals or any other information or context that helps ethically situate
your research. For help with the ethics section, feel free to ask on the
NIME forum: \url{https://forum.nime.org}.
% \end{anonsuppress}

\begin{acks}

% \begin{anonsuppress}
% This is the continuation of the previous work by the author
% A project of this breadth developed across 3 institutes and 2 countries
% cannot be carried without the support and technical knowledge of many
% skilled and passionate people.
% \end{anonsuppress}

% \begin{anonsuppress}
% A project of this breadth developed across 3 institutes and 2 countries
% cannot be carried without the support and technical knowledge of many
% skilled and passionate people.
% \end{anonsuppress}

\begin{anonsuppress}
We acknowledge the invaluable contributions of

\begin{itemize}
\tightlist
\item
  Unibo

  \begin{itemize}
  \tightlist
  \item
    Alma Labor

    \begin{itemize}
    \tightlist
    \item
      Massimiliano Fraulini and the staff of Alma Labor at the Yiversità
      of bologna for their 3D printing expertise and generosity with
      electronics equipment
    \end{itemize}
  \item
    Fisica Tecnica

    \begin{itemize}
    \tightlist
    \item
      Maurzio Chendi Fabrizio Casarini, Giulio Severo and Barbara
      Costantini
    \end{itemize}
  \end{itemize}
\item
  San Colombano

  \begin{itemize}
  \tightlist
  \item
    Catalina Vincens
  \item
    Roberto Livi
  \end{itemize}
\item
  Edinburgh

  \begin{itemize}
  \tightlist
  \item
    uCreate

    \begin{itemize}
    \tightlist
    \item
      Simeon, Stuart, Millie, and Ruth of uCreate at the Univeristy of
      Edinburgh for their support with soldering facilities.
    \end{itemize}
  \item
    ECA

    \begin{itemize}
    \tightlist
    \item
      Richard Collins and the Digital Making Staff at the Edinburgh
      College of Art for 3D printing instruction and CNC support.
    \item
      Joe Hathaway of Digital Development at the College of Art for
      providing electronics components
    \item
      St Cecilia's Jenny Nex
    \end{itemize}
  \end{itemize}
\end{itemize}

\end{anonsuppress}
\end{acks}

>>>>

@@

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
A project of this breadth developed across 3 institutes and 2 countries
cannot be carried out without the support and technical knowledge of many
skilled and passionate people.

We acknowledge the invaluable contributions of

\begin{itemize}
\item
  Unibo
  \begin{itemize}
  \item
    Alma Labor
    \begin{itemize}
    \item
      Massimiliano Fraulini and the staff of Alma Labor at the Yiversità
      of bologna for their 3D printing expertise and generosity with
      electronics equipment
    \end{itemize}
  \item
    Fisica Tecnica
    \begin{itemize}
    \item
      Maurzio Chendi Fabrizio Casarini, Giulio Severo and Barbara
      Costantini
    \end{itemize}
  \end{itemize}
\item
  San Colombano
  \begin{itemize}
  \item
    Catalina Vincens
  \item
    Roberto Livi
  \end{itemize}
\item
  Edinburgh
  \begin{itemize}
  \item
    uCreate
    \begin{itemize}    
    \item
      Simeon, Stuart, Millie, and Ruth of uCreate at the Univeristy of
      Edinburgh for their support with soldering facilities.
    \end{itemize}
  \item
    University of Edinburgh
    \begin{itemize}
    \item
      Richard Collins and the Digital Making Staff at the Edinburgh
      College of Art for 3D printing instruction and CNC support.
    \item
      Joe Hathaway of Digital Development at the College of Art for
      providing electronics components
    \item
      St Cecilia's Jenny Nex
    \end{itemize}
  \end{itemize}
\end{itemize}

\end{acks}
